# Course Project 1

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=4, fig.path="figure/",echo = TRUE)
```

## Loading and preprocessing the data
### Download dataset as dataframe
```{r}
library(readr)
url <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(url,destfile="activity.csv.zip")
df <- read_csv("activity.csv.zip")
```

## What is mean total number of steps per day
### Calculate the total number of steps per day 
```{r}
library(dplyr)
y <- df %>% group_by(date) %>% summarise(total=sum(steps))
head(y) 
```
and make a histogram.
```{r}
hist(y$total,xlab="Total number of steps taken each day",main="Histogram of total steps per day", breaks=25) 
```

### The mean of the total number of steps taken per day
```{r}
 mean(y$total, na.rm=T)
```

### The median of the total number of steps taken per day
```{r}
median(y$total, na.rm=T) 
```

## What is the average daily activity pattern? 
Make a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
library(ggplot2)
library(dplyr)
dt <- df %>% group_by(interval) %>% summarise(avesteps = mean(steps,na.rm=T)) 
        ggplot(dt,aes(interval,avesteps)) + geom_line() + 
        ggtitle("Daily activity pattern") + xlab("Interval") + ylab("Average number of steps")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
dt$interval[which.max(dt$avesteps)]
```

## Imputing missing values 

### Total number of missing values in the data set
```{r}
 na <- subset(df,is.na(df$steps))
 nrow(na)
```

### Filling in all of the missing values in the dataset.
### Creat new dataset(df2) filled the NAs with mean for that 5 min-interval
```{r}
 df2 <- df 
 head(df2)
 int <- df2$interval[is.na(df2$steps)]
 df2$steps[is.na(df2$steps)] <- dt$avesteps[dt$interval %in% int]
 head(df2)
```

### Make a histogram of the total number of steps taken each day in new data set.
```{r}
 z <- with(df2,tapply(steps,date,sum)) 
 hist(z, xlab="Total number of steps taken each day",main="Histogram of NA filled data", breaks=25) 
```

### Calculate mean of total steps per day in new data set. 
```{r}
mean(z, na.rm=T)
```

### Calculate median of total steps per day in new data set.
```{r}
median(z, na.rm=T)
```

## Are there differences in activity patterns between Weekdays and Weekends? 
### Creat a new factor variable - "weekday" and "weekend" 
```{r}
df2$weekdays <- weekdays(df2$date) 
df2$weekdays <- ifelse(df2$weekdays=="토요일"|df2$weekdays=="일요일","Weekend","Weekday")
head(df2)
```

### Make a panel plot 
containing a time series of the 5 miniute interval (x-axis) and the average number of steps, averaged all weekdays or weekend days(y-axis)
```{r}
dt2 <- df2 %>% group_by(interval,weekdays) %>% summarise(avesteps = mean(steps)) 
        ggplot(dt2,aes(interval,avesteps,group=weekdays)) + geom_line() + facet_grid(weekdays~.) + 
        ggtitle("Activity pattern between Weekdays and Weekends") + xlab("Interval") + ylab("Average number of steps")
```
